### 2017-06-24 submissions/ohbm_2017/Poster/poster.tex
Big picture plots

\documentclass[portrait,a0,final]{a0poster} % a0poster class sets the paper size
\usepackage[RGB,A0]{ScientificPosterTemplate} % RGB, Coated, Uncoated
\usepackage[english]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf} % so that ''pdflatex'' accepts .eps files
\usepackage{titlesec} % For changing the font on chapters, sections, etc.
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{lipsum} % Lorem ipsum generator
\usepackage{floatrow}

@@

%% Title: use \baselinestretch to change linespacing, \textit{} for italic text, \textcolor for colored text
% More conservative title, upright and black
{\renewcommand{\baselinestretch}{0.85} % Changes the baseline skip smaller for the title
\VeryHuge{\bfseries{\textsf{\textcolor{bleu}{Towards a better predictive model
from rest fMRI: benchmarks across multiple phenotypes}}}} % Text size for a1 posters
\par} % <- for \baselinestretch

@@

\Large{\textsf{\bfseries{\underline{Kamalaker Dadi}$^{1*}$, Darya Chyzhyk$^1$,
Alexandre Abraham$^1$, Mehdi Rahim$^1$, Bertrand Thirion$^1$,
Gael Varoquaux$^1$}}} % Text size for a1 posters

\vspace{0.01\linewidth}
\Large{\textcolor{posterBlack}{\textsf{%\bfseries{
            $^1$Parietal team, Neurospin -- I${^2}$BM -- CEA, INRIA, Paris-Saclay, France \\ $^*$kamalaker-reddy.dadi@inria.fr%}
}}}
%
\end{minipage}
\hspace{0.08\linewidth}
%\begin{minipage}{0.15\linewidth} % logo
%\vspace{0pt} % Alingns the parallel minipages on top
%\begin{flushright}
%\includegraphics[width=0.30\linewidth,
%angle=0]{figures/logos/parietal_web_page.png}
%\end{flushright}

@@

% Space according to the visual identity guidelines...
\vspace{0.04\linewidth}

@@

\section{Introduction}
Psychiatry and psychology are based on assessing individuals traits,
characterized through
behavioral testing and questionnaires. Imaging of brain activity raises the
hope of measuring
the physiological differences that underlie these psychological variations
\cite{miller}. In \cite{abraham}, we have
introduced an automated pipeline capable of learning this link across
individuals using large
cohorts of functional magnetic resonance images acquired during rest (Rest
fMRI). We present the outline of this pipeline
and how we used it to draw best practices from its application on various problems.

\vspace{0.8\sectionspace}
\section{A connectome classification pipeline}
We applied the pipeline on five datasets to i) determine the steps to obtain
the best
prediction, and ii) predict phenotypic information with good accuracy.

@@

\vspace{0.6\sectionspace}
\section{Rest fMRI datasets}

\begin{center}
    \begin{tabular}{ccc}
        \rowcolor{gray!50}
        Dataset & Subjects & Clinical question \\
        \hline\\[-4mm]
        COBRE & $65/77$ & Schizophrenia vs Control \\
        \rowcolor{gray!13}
        ADNI & $40/96$ & AD vs MCI  \\
        ADNIDOD & $89/78$& PTSD vs Control \\
        \rowcolor{gray!13}
        ACPI & $62/64$ & Marijuana use vs Control \\
        ABIDE & $402/464$ & Autism vs Control
    \end{tabular}
\end{center}
\captionof{table}{Description of the five rs-fMRI
    datasets used.
    AD - Alzheimer's Disease, MCI - Mild
    Cognitive Impairment,
    PTSD - Post Traumatic Stress Disorder.}
%\vspace{\tablespace}

\section{Pipelining choices}
    %\begin{enumerate}
    %   \item Defining Brain ROIs
    %   \item Connectivity parameterizing
    %   \item Supervised Learning: Classifiers
    %\end{enumerate}
%\vspace{\figurespace}
\begin{center}
\includegraphics[width=0.7\linewidth]{figures/only_pipeline_choices.pdf}
\end{center}
\captionof{figure}{{\bfseries\sffamily 1 -- Defining Brain ROIs} can be done using
    three pre-defined atlases: two anatomical - Automated Anatomical Labeling
    (AAL), Harvard Oxford and one functional - Bootstrap Analysis
    of Stable Clusters (BASC). Four region learning methods: two Linear
    decomposition models - Group Independent Component Analysis (Group ICA),
    Online Dictionary Learning and two Clustering models - KMeans,
    Agglomerative with Ward criterion.
    {\bfseries\sffamily 2 -- Parameterizing functional connectivity
    between ROIs}: correlation, partial correlation or tangent space embedding
    {\bfseries\sffamily 3 -- Supervised learning}: Classifiers, a
classification
    model is built to predict groups with two linear classifiers, SVC
($\ell_{1}$
    or $\ell_{2}$ penalization) and Ridge. Definition of brain regions (below). \label{fig_2}}
%\vspace{\figurespace}

%\begin{centering}
\begin{minipage}{0.22\textwidth}
\begin{minipage}{1.5\linewidth}
\begin{center}
\includegraphics[width=2.22\linewidth]{figures/rois2.pdf}
%\captionof{figure}{Definition of Brain regions. \label{fig_3}}
\end{center}
\end{minipage}
\end{minipage}
%\end{centering}
%\vspace{\figurespace}
%\begin{minipage}[t]{0.35\linewidth}
%        Here is the text
%          \end{minipage}\hfill
%            \begin{minipage}[b]{0.55\linewidth}
%                    \includegraphics[width=40cm]{figures/rois.pdf}
%                        \captionof{figure}{A wonderful picture}
%                          \end{minipage}
%

@@

@@

\begin{minipage}{0.98\textwidth} % Minipages for the footers

\large % Text size for footers

\begin{minipage}[c]{0.475\linewidth}% Footer #1
\vspace{0pt}
\begin{center}
\textcolor{posterGray}{\hrule}
\vspace{0pt}
\includegraphics[height=17mm, angle=0]{figures/logos/parietal_web_page.png}
\qquad \quad
\includegraphics[height=17mm, angle=0]{figures/logos/neurospin.jpg}
\qquad \quad
\includegraphics[height=29mm, angle=0]{figures/logos/logo-inria2.jpg}
\end{center}
\end{minipage} % No empty line before the second begin!
\hspace{0.01\linewidth}
\begin{minipage}[c]{0.575\linewidth} % Footer #2
    \begin{center}
\vspace{0pt}
\textbf{\sffamily Acknowledgments:}\\
ANR-11-BINF-0004\_NiConnect and
CATI project.
\end{center}
\end{minipage}

>>>>

\pdfminorversion=4
\documentclass[portrait,a0,final]{a0poster} % a0poster class sets the paper size
\usepackage[RGB,A0]{ScientificPosterTemplate} % RGB, Coated, Uncoated
\usepackage[english]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf} % so that ''pdflatex'' accepts .eps files
\usepackage{titlesec} % For changing the font on chapters, sections, etc.
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{lipsum} % Lorem ipsum generator
\usepackage{floatrow}

@@

%% Title: use \baselinestretch to change linespacing, \textit{} for italic text, \textcolor for colored text
% More conservative title, upright and black
{\renewcommand{\baselinestretch}{0.8} % Changes the baseline skip smaller for the title
\VeryHuge{\bfseries{\textsf{\textcolor{bleu}{Predictive models based on
functional connectivity: a benchmark across multiple datasets}}}} % Text size for a1 posters
\par} % <- for \baselinestretch

@@

\Large{\textsf{\bfseries{Kamalaker DADI$^{1}$, Alexandre ABRAHAM$^1$,
Mehdi RAHIM$^1$, Darya CHYZHYK$^1$, Bertrand THIRION$^1$,
Ga{\"e}l VAROQUAUX$^1$}}} % Text size for a1 posters

\vspace{0.01\linewidth}
\Large{\textcolor{posterBlack}{\textsf{%\bfseries{
            $^1$Parietal team, Neurospin -- CEA, INRIA, Paris-Saclay, France%}
}}}
%
\end{minipage}
\begin{minipage}{0.76\paperwidth}
\vspace{-0.035\linewidth}
\begin{flushright}
\includegraphics[height=15mm, angle=0]{figures/logos/parietal_web_page.png}
\qquad \quad
\includegraphics[height=15mm, angle=0]{figures/logos/neurospin.jpg}
\qquad \quad
\includegraphics[height=26mm, angle=0]{figures/logos/logo-inria2.jpg}
\end{flushright}
\end{minipage} % No empty line before the second begin!
%\hspace{0.01\linewidth}
%\begin{minipage}{0.95\linewidth} % logo
%    \hfill
%\vspace{0pt} % Alingns the parallel minipages on top
%\begin{flushright}
%\includegraphics[width=0.20\linewidth,
%angle=0]{figures/logos/parietal_web_page.png}
%\end{flushright}

@@

% Space according to the visual identity guidelines...
\vspace{0.03\linewidth}

@@

\section{Introduction}
\begin{itemize}
    \item Psychiatry and psychology are based on assessing individuals traits
        characterized through \textbf{behavioral testing} and
        \textbf{questionnaires}.
    \item \textbf{Imaging of brain activity} measures the physiological
        differences that underlie these \textbf{psychological
        variations}\cite{miller}.
    \item Introduction of \textbf{automated pipeline}\cite{abraham}.
        \begin{itemize}
            \item  Learning the \textbf{link} across individuals.
            \item Large cohorts of functional magnetic resonance images at
                rest \textbf{(Rest-fMRI)}.
        \end{itemize}
    \item We present the \textbf{outline} of this pipeline
        and how we used it to \textbf{draw best practices} from the
        application of pipeline on
        various problems.
\end{itemize}

\vspace{0.3\sectionspace}
\section{A connectome classification pipeline}
%We applied the pipeline on five datasets to i) determine the steps to obtain
%the best
%prediction, and ii) predict phenotypic information with good accuracy.

@@

\vspace{0.0991\sectionspace}
\section{Rest fMRI datasets}

\begin{center}
    \begin{tabular}{ccc}
        \rowcolor{gray!50}
        Dataset & Subjects & Clinical question \\
        \hline\\[-4mm]
        COBRE & $65/77$ & Schizophrenia vs Control \\
        \rowcolor{gray!13}
        ADNI & $40/96$ & AD vs MCI  \\
        ADNIDOD & $89/78$& PTSD vs Control \\
        \rowcolor{gray!13}
        ACPI & $62/64$ & Marijuana use vs Control \\
        ABIDE & $402/464$ & Autism vs Control
    \end{tabular}
\end{center}
\captionof{table}{Description of the \textbf{five rs-fMRI
    datasets} used.
    AD - Alzheimer's Disease, MCI - Mild
    Cognitive Impairment,
    PTSD - Post Traumatic Stress Disorder.}
%\vspace{\tablespace}

\section{Pipelining choices}
    %\begin{enumerate}
    %   \item Defining Brain ROIs
    %   \item Connectivity parameterizing
    %   \item Supervised Learning: Classifiers
    %\end{enumerate}
%\vspace{\figurespace}
\begin{center}
\includegraphics[width=0.7\linewidth]{figures/only_pipeline_choices2.pdf}
\end{center}
\captionof{figure}{{\bfseries\sffamily 1 -- Defining Brain ROIs} can be done using
    three pre-defined atlases: two anatomical - Automated Anatomical Labeling
    (AAL), Harvard Oxford and one functional - Bootstrap Analysis
    of Stable Clusters (BASC). Four region learning methods: two Linear
    decomposition models - Group Independent Component Analysis (Group ICA),
    Online Dictionary Learning and two Clustering models - KMeans,
    Agglomerative with Ward criterion.
    {\bfseries\sffamily 2 -- Parameterizing functional connectivity
    between ROIs}: correlation, partial correlation or tangent space embedding
    {\bfseries\sffamily 3 -- Supervised learning}: Classifiers, a
classification
    model is built to predict groups with two linear classifiers, SVC
($\ell_{1}$
    or $\ell_{2}$ penalization) and Ridge. Definition of brain regions (below). \label{fig_2}}
%\vspace{\figurespace}

%\begin{centering}
\begin{minipage}{0.38\linewidth}
\begin{center}
\includegraphics[width=2.5\linewidth]{figures/rois2.pdf}
%\captionof{figure}{Definition of Brain regions. \label{fig_3}}
\end{center}
\end{minipage}
%\end{centering}
%\vspace{\figurespace}
%\begin{minipage}[t]{0.35\linewidth}
%        Here is the text
%          \end{minipage}\hfill
%            \begin{minipage}[b]{0.55\linewidth}
%                    \includegraphics[width=40cm]{figures/rois.pdf}
%                        \captionof{figure}{A wonderful picture}
%                          \end{minipage}
%

@@

\begin{spacing}{0.7}
\begin{minipage}[c]{0.675\linewidth}
    \begin{center}
\vspace{0.1\linewidth}
\textbf{\large Acknowledgments:}\\
\vspace{0.02\linewidth}
\large{ANR-11-BINF-0004\_NiConnect and CATI project}.
%\vspace{0.02\linewidth}
%\textcolor{posterGray}{\hrule}
%\vspace{0.02\textwidth}
%See Also Posters: \textbf{$\#1656$, $\#1829$, $\#3934$}
\end{center}

\end{minipage}
\end{spacing}

\begin{minipage}[c]{0.995\linewidth}
\vspace{0pt}
\begin{flushright}
\vspace{-0.03\linewidth}
\includegraphics[height=64mm, angle=0]{figures/logos/nilearn-logo.png}
\end{flushright}
\end{minipage}

@@

%\begin{minipage}{0.98\textwidth} % Minipages for the footers

%\large % Text size for footers

%\begin{minipage}[c]{0.475\linewidth}% Footer #1
%\vspace{0pt}
%\begin{center}
%\textcolor{posterGray}{\hrule}
%\vspace{0pt}
%\includegraphics[height=17mm, angle=0]{figures/logos/parietal_web_page.png}
%\qquad \quad
%\includegraphics[height=17mm, angle=0]{figures/logos/neurospin.jpg}
%\qquad \quad
%\includegraphics[height=29mm, angle=0]{figures/logos/logo-inria2.jpg}
%\end{center}
%\end{minipage} % No empty line before the second begin!
%\hspace{0.01\linewidth}
%\begin{minipage}[c]{0.575\linewidth} % Footer #2
%    \begin{center}
%\vspace{0pt}
%\textbf{\sffamily Acknowledgments:}\\
%ANR-11-BINF-0004\_NiConnect and
%CATI project.
%\end{center}
%\end{minipage}

%\end{minipage}
